Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-01 analysis/paper/hotspots-paper.Rmd
added code_folding to Rmd

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
linkReferences: true
link-citations: true
output: 
  - github_document:
      html_preview: false
      toc: true
      toc_depth: 3
  - bookdown::html_document2  
---

@@

Undetermined: Chr 7, Chr 11

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
linkReferences: true
link-citations: true
output: 
  bookdown::html_document2:
  code_folding: hide  
---

@@

Undetermined (right now): Chr 7, Chr 11
